---
title: "Domains - Exploratory Analysis"
author: "Nick Allen"
date: "October 8, 2014"
output:
  html_document:
    fig_height: 6
    fig_width: 8.5
    toc: yes
---

```{r, echo=FALSE, message=FALSE}
setwd ("..")
library (ProjectTemplate)
load.project ()
```

### Data

There is an overwhelming number of 'legit' domains versus malicious.  This severe class imbalance will need to be dealt with as it will negatively impact model training.

```{r}
domains [, .N, by = type]
```

### Features

#### Domain Length

The number of characters of the domain itself seems to be a significant differentiator between legitimate and malicious domains.  Malicous domains tend to have much longer domain names.

```{r}
ggplot (domains, aes (length, fill = type)) + 
    geom_density () + 
    facet_wrap (~ type, ncol = 1)
```

The average malicious domain is about twice as long as the benign one.

```{r}
domains [, list (mean = mean (length), median = median (length)), by = type]
```

#### Dictionary Words

Malicious domains tend to have far fewer valid dictionary words embedded within the domain.  The number of dictionary words as a fraction of the total number of substrings is used to control for longer domain names.

```{r}
ggplot (domains, aes (dictionary, fill=type)) + 
    geom_density () +
    facet_wrap (~ type, ncol = 1)
```

For legit domains, roughly `r percent (domains [type == "legit", mean (dictionary)])` of all domain substrings are valid dictionary words.  For malicious domains only about `r percent (domains [type == "malicious", mean (dictionary)])` are valid dictionary words.  This is a striking difference.

```{r}
domains [, mean (dictionary), by = type]
```





