---
title: "Domains - Exploratory Analysis"
author: "Nick Allen"
date: "October 8, 2014"
output: html_document
---

```{r}
setwd ("..")
library (ProjectTemplate)
load.project ()
```

### Data 

There is an overwhelming number of 'legit' domains versus malicious.  This severe class imbalance will need to be dealt with as it will negatively impact model training.

```{r}
ggplot (domains, aes (x=factor(1), fill=type)) + geom_bar (width=1) + coord_polar (theta="y")
```

#### Domain Length

The number of characters of the domain itself seems to be a significant differentiator between legitimate and malicious domains.  Malicous domains tend to have much longer domain names.

```{r}
ggplot (domains, aes (length, fill = type)) + geom_density () + facet_wrap (~ type, ncol = 1)
```

The average malicious domain is about twice as long as the benign one.

```{r}
domains [, list (mean  = mean (length)), by = type]
```

#### Dictionary Word Count

```{r}
ggplot (domains, aes (dictionary, fill=type, alpha=0.5)) + geom_density()
```

```{r}
domains [, mean (dictionary), by = type]
```





